Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-21 paper/main.tex
backing up progress

\subsubsection*{Fitness tracking using Fitbit devices}

@@

\subsubsection*{Processing Fitbit data}
\paragraph*{Raw metrics.}
\paragraph*{Comparing recent versus baseline measurements.}

>>>>

\subsubsection*{Fitness tracking using Fitbit devices}
To gain access to our study, participants provided us with access to
all data associated with their Fitbit account from the
year (365 calendar days) up to and including the day they accepted the
HIT.  We filtered out all identifiable information (e.g., participant names, GPS
coordinates, etc.) prior to importing their data.

\subsubsection*{Collecting and processing Fitbit data}

The fitness
tracking data associated with participants' Fitbit accounts varied in
scope and duration
according to which device the participant owned (Fig.~\ref{fig:devices}), how often the
participant wore (and/or synced) their tracking device, and how long they had owned their
device.  For example, while all participants' devices supported basic
activity metrics such as daily step counts, only a subset of the
devices with heart rate monitoring capabilities provided information
about workout intensity, resting heart rate, and other related
measures.

@@

Across all devices, we collected the following information: heart
rate data, sleep tracking data, logged bodyweight measurements, logged
nutrition measurements, Fitbit account and device settings, and
activity metrics.

\paragraph{Heart rate.}  If available, we extracted all
heart rate data collected by participants' Fitbit device(s) and associated with
their Fitbit profile.  Depending on the specific device model(s) and
settings, this included second-by-second, minute-by-minute, daily
summary, weekly summary, and/or monthly summary heart rate
information.  These summaries include information about participants' average
heart rates, and the amount of time they were estimated to have spent in
different ``heart rate zones'' (rest, out-of-range, fat burn, cardio, or
peak, as defined by their Fitbit profile), as well as an estimate of the number of estimated calories
burned while in each heart rate zone.

\paragraph{Sleep.}  If available, we extracted all sleep data collected
by participants' Fitbit device(s).  Depending on the specific device
model(s) and settings, this included nightly estimates of the duration
and quality of sleep, as well as the amount of time spent in each
sleep stage (awake, REM, light, or deep).

\paragraph{Weight.}  If available, we extracted any weight-related
information affiliated with particiants' Fitbit accounts within 1 year
prior to enrolling in our study.  Depending on their specific device model(s) and
settings, this included their weight, body mass index, and/or body fat
percentage.

\paragraph{Nutrition.} If available, we extracted any nutrition-related
information affiliated with particiants' Fitbit accounts within 1 year
prior to enrolling in our study. Depending on their specific account
settings and usage behaviors, this
included a log of the specific foods they had eaten (and logged)
over the past year, and the amount of water consumed each day.

\paragraph{Account and device settings.}  We extracted any settings
associated with participants' Fitbit accounts to determine (a) which
device(s) and model(s) are associated with their Fitbit account, (b)
time(s) when their device(s) were last synced, and (c) battery
level(s).

\paragraph{Activity metrics.}  If available, we extracted any
activity-related information affiliated with particiants' Fitbit
accounts within 1 year prior to enrolling in our study.  Depending on
their specific device model(s) and settings, this included: daily step
counts; daily amount of time spent in each activity level (sedentary,
lightly active, fairly active, or very active, as defined by their
account settings and preferences); daily number of floors climbed;
daily elevation change; and daily total distance traveled.

\subsubsection*{Comparing recent versus baseline measurements.}
We were interested in separating out potential associations between
\textit{absolute} fitness metrics and \textit{relative} metrics.  To
this end, in addition to assessing potential raw
(absolute) fitness metrics, we also defined a simple measure of recent
changes in those metrics, relative to a baseline.  We

In order to study
